Comparing human and model-based forecasts of COVID-19 in Germany and Poland

### 2021-10-13 manuscript/manuscript.Rmd
update manuscript

@@

## Performance across locations (maybe not a separate section or more nuance)

Generally, trends in overall performance were similar across locations (Figure S1). Notably,the convolution model performed better, when assessed by both median and mean WIS, in Germany than Poland indicating a stronger connection between observed cases and deaths. Due to the differing population sizes and numbers of notifications in Germany and Poland absolute scores were difficult to compare directly  (Figure S1).

All model-based predictions, but not the crowd forecasts, were noticeably sharper in Poland than in Germany (Figure S1), in line with their smaller overall WIS values. Crowd forecasts for cases (but not for deaths) were approximately equally sharp in Poland and in Germany. For both cases and deaths, forecasts tended to be lower relative to observed values in Poland than in Germany, with bias values lower for all forecasts in Poland than in Germany (except crowd forecasts of cases, Figure S1F).

>>>>

Generally, trends in overall performance were broadly similar across locations (Figure XX). However, relative to the Hub ensemble, the crowd forecasts performed better in Germany than in Poland and the renewal model better in Poland than in Germany (Figure XXA, XXG).

@@
